Distinguishing Between Spin-Aligned and Isotropic Binary Black Hole Populations in Advanced LIGO

### 2017-01-23 paper/AlignedIsotropicGW.tex
Update AlignedIsotropicGW.tex

\citet{Miller2015} summarises the current best \ac{EM} constraints on
the black hole spin distribution; it is consistent with flat but could
be increasing toward large spins (\fixme{Cole: can you confirm and
  summarise better?}).

>>>>

In order to perform our analysis we need to select models for the distribution of the dimensionless spin parameters of stellar-mass black holes.  Data for such model selection is sparse.  \citet{2015PhR...548....1M} give current estimates of the spin parameters for stellar-mass black holes, obtained using disk reflection and/or disk continuum methods.

Most of the systems studied are low-mass X-ray binaries (i.e., the donor star has a mass $M_{\rm donor}<1~M_\odot$) rather than the high-mass X-ray binaries that are likely to be the progenitors of double black hole binaries.  In addition, there are substantial systematic errors that can complicate either type of analysis (see \citealt{2015PhR...548....1M} for a discussion). Nonetheless, if we take the reported spin magnitudes as representative then we find that there is a preference for high spins; for example, 14 of the 19 systems with reported spins have spin parameters in excess of 0.5.  The masses and spin parameters of stellar-mass black holes are unlikely to be altered significantly by accetion (low-mass donors simply do not have enough mass and high-mass donors have a very short phase in which they transfer mass; a variant of this long-standing argument was presented by \citealt{1999MNRAS.305..654K}).  Thus the current spin parameters probably are close to their values upon core collapse.  We emphasize, however, that the specific processes involved in the production of black hole binaries could alter the spin distribution of those holes: for example, close tidal interactions could spin up the core, or stripping of the envelope could reduce the available angular momentum.

With this in mind, we do our analysis using three straw-man spin distributions for spin parameters from $a/M=0$ to 1: flat ($P(a/M)=1$); rising ($P(a/M)=2a/M$); and falling ($P(a/M)=2(1-a/M)$).  These are not meant to represent any particular physical model, and indeed neither observations nor population synthesis codes can authoritatively suggest {\it any} particular spin distribution.  This does, however, allow us to see how sensitive the $\chieff$ distribution is to spin alignment models given uncertainties about the spin magnitudes.
